Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective

### 2015-05-05 thesis/paper.tex
Review serialport

%%Describe the change 
The final new feature of the API was the inclusion of axserialport. This part of the API allows API users to connect various devices to their cameras through the use of a serial port. This effectively allows users to integrate multiple kinds of devices to create their own unique solutions. In the previous version of the API there was no ability to connect to devices outside of the VMS.

%%Relate it to Categories
The inclusion of this new feature was once again determined to be an enhancive change as it involved the addition of a brand new feature. No relevant sub-categories were found.

Our interviewee described scenarios whereby a camera could be used with external devices to create, for example, a ticketing system which reacts to users interacting with it in close proximity. This was just one scenario in which users might wish to use the camera with other devices. As such it was included in the new API to meet the demand of the API users.

%%Real category
Given this information, we concluded that we were correct in deciding that this change was also enhancive. Again, we were also correct in the assumption that there were no suitable sub-categories for this change.

>>>>

%%Describe the change 
The addition of axserialport allows API users to connect various devices to their cameras by through the serial port. This allows users to integrate multiple devices to create their own unique solutions. In version 1.4 of the API, there was no possibility to connect external devices to the camera.

%%Relate it to Categories
The addition of this module was determined to be an enhancive change, as it involved the addition of a new feature. No relevant secondary category were identified.

%%What she said
The addition of axserialport was requested by API users. A possible use case, which was given during the interiew involved a ticketing system which allows for joint analysis of data from both devices. As such it was included in version 2.0, to meet the demand of the API users.

%%Real category
Given this information, we concluded that we were correct in predicting that this change was enhancive. The prediction of the secondary category was also correct.
